Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-06 paper/paper.tex
Working on comments

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits
of the integer and fractional part, respectively.  Note that $G(z)$ is a
discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
model of the plant must be discretized to obtain the discrete equivalent
coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization %\red{[pls say how]}
. Although there are several discretization methods available in the literature~\cite{Franklin15}, the
zero-order hold (ZOH) discretization is more suitable for representing the
sampling processes that are typically employed by hybrid
systems~\cite{istepanian2012digital} 
\red{[but the ZOH is for the DAC, not for the ADC?]}.

@@

A model for $\Delta{G_{Q}(z)}$ that can represent the quantization
noise effect in the plant output, and consequently the closed-loop system
output, is proposed.  
\red{[eliminate next:] 
For convenience, the parametric uncertainties will be described here.}

@@

\begin{mylemma} \cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH. It is equivalent at the sample times ({\it i.e.} $kT$ to the continuous transfer function $G(s)$ driven by ZOH.  This pulse transfer
function can be computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
\end{mylemma}
\red{[Here the dependence on the sampling time T needs to appear somewhere.]} 
\green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
\red{[ok, then let's call it $G(z,T)$ as I suggested earlier.]}

@@

Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
effect on the plant transfer function demands an estimation of the variance
of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
methodology presented by~\cite{widrow2008quantization}
is used.  The authors provide an algorithm for computing the mean square of
the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
contribution can be represented by a white noise with zero mean
(Assumption~\ref{whitenoise}), the mean square can be considered as the
variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
%
\begin{equation}
\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
\end{equation}
%
\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors \red{[define scale factors]} for the
quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.

>>>>

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits
of the integer and fractional part, respectively.  Note that $G(z)$ is a
discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
model of the plant must be discretized to obtain the discrete equivalent
coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization %\red{[pls say how]}
. Although there are several discretization methods available in the literature~\cite{Franklin15}, the
zero-order hold (ZOH) discretization is more suitable for representing the
sampling and holding processes that are typically employed by hybrid
systems~\cite{istepanian2012digital}, i.e. the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.% {\item \red{[but the ZOH is for the DAC, not for the ADC?]}.

@@

A model for $\Delta{G_{Q}(z)}$ that can represent the quantization
noise effect in the plant output, and consequently the closed-loop system
output, is proposed.  
%\red{[eliminate next:] 
%For convenience, the parametric uncertainties will be described here.}

@@

\begin{mylemma} \cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH. It is equivalent at the sample times ({\it i.e.} $kT$ to the continuous transfer function $G(s)$ driven by ZOH.  This pulse transfer
function can be computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}

For convenience, we will use only the notation $G(z)$ for represent the pulse transfer function.
\end{mylemma}
%\red{[Here the dependence on the sampling time T needs to appear somewhere.]} 
%\green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
%\red{[ok, then let's call it $G(z,T)$ as I suggested earlier.]}

@@

Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
effect on the plant transfer function demands an estimation of the variance
of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
methodology presented by~\cite{widrow2008quantization}
is used.  The authors provide an algorithm for computing the mean square of
the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
contribution can be represented by a white noise with zero mean
(Assumption~\ref{whitenoise}), the mean square can be considered as the
variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
%
\begin{equation}
\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
\end{equation}
%
\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]} 
for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
